Deep Learning for Automatic Speech Recognition

### 2015-04-30 Paper/Paper.tex
Minor changes

\paragraph{} Based on this formalism, \cite{DBLP:journals/taslp/DahlYDA12} chose to use a pre-trained \DNN to estimate $\cprob{q_t}{x_t}$ using MFCCs as DNN inputs and taking the senone posterior probabilities as DNN outputs. The transitioning between events is best modeled by hidden markov model whose notation, $\pi, a$, and $q$ appears in Eqn. (\ref{eqn:lm:def}). Now that we have an overview of the general CD-DNN-HMM architecture, we can look at how \cite{DBLP:journals/taslp/DahlYDA12} train their model.

@@

\paragraph{} Over the past few years, Convolutional Neural Networks have proven to be highly successful in image recognition tasks. Not only have they achieved the highest results on the MNIST character recognition dataset\cite{DBLP:journals/corr/abs-1003-0358}, but they've even proven to outstrip hand-crafted object recognition systems on the much more complex ImageNet dataset \cite{DBLP:conf/nips/KrizhevskySH12}. This success primarily originates from the networks ability to replicate lower-resolution features across the input space. They have also previously been used for speech recognition in \cite{hau2011exploring}, but without great success. There they claim that while CNNs look promising for ASR, just taking the same structure as one built for image recognition will not suffice. For example, in that work they used convolutions performed along the time axis. \cite{DBLP:journals/taslp/Abdel-HamidMJDPY14} attempts to address these concerns and instead design a CNN specifically for ASR.

@@

\cite{DBLP:journals/taslp/Abdel-HamidMJDPY14} use just one convolution and pooling ply, and two 1000 unit, fully connected hidden layers in their experimental section. They also make use of 150 feature maps for full weight sharing, and 80 feature maps for limited weight sharing. As mentioned above, they do see some slight improvements in the LWS scheme. They do not explain their hardware resources or how long their training time took. Yet for a little perspective, in \cite{hau2011exploring} they used a somewhat similarly structured CNN which required less than a day to train. There's is less complicated than the one present in \cite{DBLP:journals/taslp/Abdel-HamidMJDPY14}, so slightly longer training times would not be surprising.

@@

\paragraph{} Both \cite{DBLP:journals/taslp/DahlYDA12} and \cite{DBLP:journals/taslp/Abdel-HamidMJDPY14} have shown that neural network architectures exhibit better performance over Gaussian mixture models. \cite{DBLP:journals/taslp/DahlYDA12} believes that a more capable first layer model provided by mean-covariance restricted Boltzmann machines will increase performance, while \cite{DBLP:journals/taslp/Abdel-HamidMJDPY14} plans to investigate unexpected improvements in large-scale speech recognition where they were absent in phone recognition tasks when using convolutional restricted Boltzmann machines. Both routes seem promising and are likely to produce improved error rates.

>>>>

\paragraph{} Based on this formalism, \cite{DBLP:journals/taslp/DahlYDA12} chose to use a pre-trained \DNN to estimate $\cprob{q_t}{x_t}$ using MFCCs as DNN inputs and taking the senone posterior probabilities as DNN outputs. The transitioning between events is best modeled by a \HMM whose notation, $\pi, a$, and $q$ appears in Eqn. (\ref{eqn:lm:def}). Now that we have an overview of the general CD-DNN-HMM architecture, we can look at how \cite{DBLP:journals/taslp/DahlYDA12} train their model.

@@

\paragraph{} Over the past few years, Convolutional Neural Networks have proven to be highly successful in image recognition tasks. Not only have they achieved the highest results on the MNIST character recognition dataset \cite{DBLP:journals/corr/abs-1003-0358}, but they've even proven to outstrip hand-crafted object recognition systems on the much more complex ImageNet dataset \cite{DBLP:conf/nips/KrizhevskySH12}. This success primarily originates from the networks ability to replicate lower-resolution features across the input space. They have also previously been used for speech recognition in \cite{hau2011exploring}, but without great success. There they claim that while CNNs look promising for ASR, just taking the same structure as one built for image recognition will not suffice. For example, in that work they used convolutions performed along the time axis. \cite{DBLP:journals/taslp/Abdel-HamidMJDPY14} attempts to address these concerns and instead design a CNN specifically for ASR.

@@

\cite{DBLP:journals/taslp/Abdel-HamidMJDPY14} use just one convolution and pooling ply, and two 1000 unit, fully connected hidden layers in their experimental section. They also make use of 150 feature maps for full weight sharing, and 80 feature maps for limited weight sharing. As mentioned above, they do see some slight improvements in the LWS scheme. They do not explain their hardware resources or how long their training time took. Yet for a little perspective, in \cite{hau2011exploring} they used a somewhat similarly structured CNN which required less than a day to train. Their's is less complicated than the one present in \cite{DBLP:journals/taslp/Abdel-HamidMJDPY14}, so slightly longer training times would not be surprising.

@@

\paragraph{} Both \cite{DBLP:journals/taslp/DahlYDA12} and \cite{DBLP:journals/taslp/Abdel-HamidMJDPY14} have shown that neural network architectures exhibit better performance over Gaussian Mixture Models. \cite{DBLP:journals/taslp/DahlYDA12} believes that a more capable first layer model provided by mean-covariance restricted Boltzmann machines will increase performance, while \cite{DBLP:journals/taslp/Abdel-HamidMJDPY14} plans to investigate unexpected improvements in large-scale speech recognition where they were absent in phone recognition tasks when using convolutional restricted Boltzmann machines. Both routes seem promising and are likely to produce improved error rates.
